TBD

### 2021-03-10 outputs/paper/paper.Rmd
Add dumbbell chart

library(tidyverse)
library(ggplot2)

library(ggthemes)
library(kableExtra)
library(janitor)
library(dplyr)
```

@@

### Merge all wallets and returned wallets with no money
dfMergedNoMoney <-
  merge(x = dfNoMoney, y = dfReturnedNoMoney, by = "country_2", all.x = TRUE) %>%
  mutate(rate = round(n.y / n.x * 100, 2)) %>%
  rename(country = "country_2") %>%
  rename(total = "n.x") %>%
  rename(returned = "n.y")

### Merge all wallets and returned wallets with money
dfMergedMoney <-
  merge(x = dfMoney, y = dfReturnedMoney, by = "country_2", all.x = TRUE) %>%
  mutate(rate = round(n.y / n.x * 100, 2)) %>%
  rename(country = "country_2") %>%
  rename(total = "n.x") %>%
  rename(returned = "n.y")

@@

### Dumbbell Plot

dfSample <- data.frame(country = c("A", "B", "c", "D", "E"), 
                       noMoney = c(20, 40, 10, 30, 50), 
                       money = c(70, 50, 30, 60, 80))

ggplot(dfSample, aes(y = country, x = noMoney, xend = money)) +
  geom_dumbbell(size = 3, 
                color = "#e3e2e1",
                colour_x = "#FFA500", 
                colour_xend = "#FF0000",
                dot_guide=TRUE, dot_guide_size=0.25) +
  labs(x=NULL, y=NULL, title="ggplot2 geom_dumbbell with dot guide") +
  theme_minimal() +
  theme(panel.grid.major.x=element_line(size=0.02))

>>>>

library(tidyverse)
library(ggplot2)
library(ggalt)
library(ggthemes)
library(kableExtra)
library(janitor)
library(dplyr)
```

@@

### Merge all wallets and returned wallets with no money
dfMergedNoMoney <-
  merge(x = dfNoMoney, y = dfReturnedNoMoney, by = "country_2", all.x = TRUE) %>%
  mutate(rating = round(n.y / n.x * 100, 2)) %>%
  rename(country = "country_2") %>%
  rename(total = "n.x") %>%
  rename(returned = "n.y")

### Merge all wallets and returned wallets with money
dfMergedMoney <-
  merge(x = dfMoney, y = dfReturnedMoney, by = "country_2", all.x = TRUE) %>%
  mutate(rating = round(n.y / n.x * 100, 2)) %>%
  rename(country = "country_2") %>%
  rename(total = "n.x") %>%
  rename(returned = "n.y")

@@

### Dumbbell Plot
dfRatings <- 
  data.frame(country = dfMergedNoMoney$country,
             noMoney = dfMergedNoMoney$rating,
             money = dfMergedMoney$rating) %>%
  arrange(desc(noMoney))

### Reorder factor levels
dfRatings$country <- reorder(dfRatings$country, dfRatings$noMoney)

ggplot(dfRatings, aes(y = country, x = noMoney, xend = money)) +
  geom_dumbbell(size = 2, 
                color = "#e3e2e1",
                colour_x = "#FFA500", 
                colour_xend = "#FF0000",
                dot_guide = TRUE, 
                dot_guide_size = 0.05,
                show.legend = TRUE) +
                # TODO: Fix legend 
  labs(x = NULL, y = NULL, title = "Share of wallets reported by country") +
  theme_minimal() +
  scale_color_manual(name = "", values = c("red", "blue") ) +
  theme(panel.grid.major.x = element_line(size = 0.02))
